---
title: "EMG4_preprocessing_data"
author: "Marijn Struiksma, Li Kloostra"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: yes
    fig_width: 5
    fig_height: 3.5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_knit$set(root.dir = "O:/Research/GW/Projects/Jvb-studentprojects/EMG4")
```

## Overview

This document contains the preparation of the EMG4 data for the Multilevel analysis.

```{r message=FALSE, warning=FALSE }
library(readxl)
library(sjPlot)
library(tidyverse)
```

# check whole trial data
```{r load whole trial data, echo=FALSE}
whole_trial_data <- read_excel(paste0(getwd(), "/Matlab/results_paper/EMG4_Bin_whole_trial_60sjs.xlsx"))

```

check number of rows per sjCode
```{r check nr of rows}
# check number of rows per sjCode, should be 64, 
# except for 2924 for whom Markertrial 32 is excluded, 
# see data_check_preparation_notes
table(whole_trial_data$sjCode)  
# check number of rows/trials per Markertrial. should be max 60 for all 51 Markertrials. 
# Could also be lower if a trial is excluded, see comment about Markertrial 32.
table(whole_trial_data$Markertrial)  
MissingMarkertrials <- whole_trial_data %>% 
  select(sjCode, Markertrial) %>% 
  group_by(Markertrial) %>% 
  summarise(Freq = n()) %>% 
  filter(Freq != 60)
table(MissingMarkertrials)

# check number of trials per MoralityCondition, should be max 32*60=1920 per condition
table(whole_trial_data$MoralityCondition)  
# check number of trials per StateAdjectiveCondition, should be max 32*60=1920 per condition
table(whole_trial_data$StateAdjectiveCondition)  
# Baseline should be between 500 and 2000
table(whole_trial_data$Baseline) 
summary(whole_trial_data$Baseline)


# Identify a time bin with extreme outlier 
x <- whole_trial_data %>% 
  filter(Markertrial == 45 & MoralityCondition== 103 & StateAdjectiveCondition ==105)  %>% 
  select(sjCode,CorrPr100ms_288)
mean <- mean(x$CorrPr100ms_288)
sd <- sd(x$CorrPr100ms_288)
outlier <- x %>% 
  filter(sjCode == 8800)
(outlier$CorrPr100ms_288-mean)/sd
# Participant 8800 has an extreme outlier (z=3.75) at trial 45 in time bin 288. 
# This data point will be removed from the whole trial figures.

```

# Load data from all 3 segments

```{r load all data,include=F, message=F}
mor_data_raw <- read_xlsx(paste0(getwd(), "/Matlab/results_paper/EMG4_Bin_Morality_60sjs.xlsx"))

adj_data_raw <- read_xlsx(paste0(getwd(),"/Matlab/results_paper/EMG4_Bin_StateAdjective_60sjs.xlsx"))

reason_data_raw <- read_xlsx(paste0(getwd(),"/Matlab/results_paper/EMG4_Bin_AffectReason_60sjs.xlsx"))
```

```{r check dataframes, include=F}
head(mor_data_raw)
head(adj_data_raw)
head(reason_data_raw)
```

```{r means per participant,include=F,message=F}
mor_means <- mor_data_raw %>%
  dplyr::select(sjCode, Markertrial, MoralityCondition, StateAdjectiveCondition, MoralityCorrPr100ms_1:MoralityCorrPr100ms_50) %>%
  rowwise(sjCode) %>% 
  mutate(MeanMorCorrPrTrial = mean(c_across(MoralityCorrPr100ms_1:MoralityCorrPr100ms_50))) %>% 
  select(sjCode, Markertrial, MoralityCondition, StateAdjectiveCondition, MeanMorCorrPrTrial)

adj_means <- adj_data_raw %>% 
  dplyr::select(sjCode, Markertrial, MoralityCondition, StateAdjectiveCondition, StateAdjectiveCorrPr100ms_1:StateAdjectiveCorrPr100ms_15) %>%
  rowwise(sjCode) %>% 
  mutate(MeanStateAdjCorrPrTrial = mean(c_across(StateAdjectiveCorrPr100ms_1:StateAdjectiveCorrPr100ms_15))) %>% 
  select(sjCode, Markertrial, MoralityCondition, StateAdjectiveCondition, MeanStateAdjCorrPrTrial)

reason_means <- reason_data_raw %>%
  dplyr::select(sjCode, Markertrial, MoralityCondition, StateAdjectiveCondition,   AffectReasonCorrPr100ms_1:AffectReasonCorrPr100ms_25) %>%
  rowwise(sjCode) %>% 
  mutate(MeanAffectReasonCorrPrTrial = mean(c_across(AffectReasonCorrPr100ms_1:AffectReasonCorrPr100ms_25))) %>% 
  select(sjCode, Markertrial, MoralityCondition, StateAdjectiveCondition, MeanAffectReasonCorrPrTrial)
```

```{r check means dfs, include=F}
head(mor_means)
head(adj_means)
head(reason_means)
```

## Scatterplot:
<!-- each PP has 2 data points (1 mean per Morality Condition)  -->
```{r scatterplot mean corr per participant x mor condition, fig.cap = "Participants' mean corrugator activation during the morality segment, per Morality Condition", echo=FALSE, message=F}
mor_means %>%
  ggplot(aes(x = as.numeric(MoralityCondition),
           y = MeanMorCorrPrTrial)) +
  geom_smooth(method = 'lm',
              se = FALSE,
              linewidth = 0.5,
              alpha = 0.8) + # to add regression line
  geom_smooth(method = 'lm') +  # add 95% confidence region
  scale_x_continuous(n.breaks = 2, labels = c('Moral', 'Immoral')) +
  scale_y_continuous(trans = 'log10', n.breaks = 8) +
    geom_point() +
  labs(x = "Morality Condition",
       y = "Corrugator activity (% of baseline)")

```


## Preprocessing

Preprocessing is needed to transform the data from wide to long format based on the 100ms bins for the corrugator response. 
The relevant variables are computed for the different conditions. 
Another MoralityValence variable is computed to estimate the final no-intercept model. 
Furthermore, we've computed linear, quadratic and cubic time trends for each condition (moral, immoral).

# 1. Morality segment

```{r eval=TRUE}

# convert from wide to long format for time and select only corrugator
mor_long <- mor_data_raw %>%
  select(!starts_with("MoralityZygoPr100ms")) %>% 
  pivot_longer( 
    cols = starts_with("MoralityCorrPr100ms"),
    names_to = "time",
    names_prefix = "MoralityCorrPr100ms_",
    names_transform = list(time = as.integer),
    values_to = "Morality_response"
  )
str(mor_long)

# moral(102)* pos(104), neg(105) = 608, 710 
# immoral(103)* pos(104), neg(105) = 712, 815

# compute relevant factors for the analysis
mor_long <- mor_long %>% 
  mutate(MoralityValence = MoralityCondition*StateAdjectiveCondition-10000)

#compute linear, quadratic and cubic time in order to compute time trends per condition
linear_time_centered <- (mor_long$time-25.5)/10
unique(linear_time_centered)
quadratic_time_centered <- linear_time_centered*linear_time_centered
cubic_time_centered <- linear_time_centered*quadratic_time_centered

#compute time trends per condition and filter only the included trials based on incCorr and incZygo
mor_long_inc <- mor_long %>% 
  mutate(t1_moral = ifelse(MoralityCondition == 102, linear_time_centered, 0)) %>%  
  mutate(t2_moral = ifelse(MoralityCondition == 102, quadratic_time_centered, 0)) %>%  
  mutate(t3_moral = ifelse(MoralityCondition == 102, cubic_time_centered, 0)) %>% 
  mutate(t1_immoral = ifelse(MoralityCondition == 103, linear_time_centered, 0)) %>%  
  mutate(t2_immoral = ifelse(MoralityCondition == 103, quadratic_time_centered, 0)) %>%  
  mutate(t3_immoral = ifelse(MoralityCondition == 103, cubic_time_centered, 0)) %>% 
  filter((incCorr==1)&(incZygo==1))

#compute the % of data loss after baseline selection
perc_inc_data = 100-(dim(mor_long_inc)[1]/dim(mor_long)[1])*100
perc_inc_data
```

The baseline procedure has resulted in an exclusion of `r perc_inc_data`% of the data.

```{r saving the morality data, eval=FALSE, echo=FALSE}
# saving the long data file
write_csv(mor_long_inc, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_morality_trial_data_27-Jun-2023_60pp_preprocessed.csv"))

save(mor_long_inc, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_morality_trial_data_27-Jun-2023_60pp_preprocessed.RData"))
```

# 2. State Adjective segment

```{r eval=FALSE}

# convert from wide to long format for time and select only corrugator
adj_long <- adj_data_raw %>%
  dplyr::select(!starts_with("StateAdjectiveZygoPr100ms")) %>% 
  pivot_longer( 
    cols = starts_with("StateAdjectiveCorrPr100ms"),
    names_to = "time",
    names_prefix = "StateAdjectiveCorrPr100ms_",
    names_transform = list(time = as.integer),
    values_to = "StateAdjective_response"
  )
str(adj_long)

# moral(102)* pos(104), neg(105) = 608, 710 
# immoral(103)* pos(104), neg(105) = 712, 815

# compute relevant factors for the analysis
adj_long <- adj_long %>% 
  mutate(MoralityValence = MoralityCondition*StateAdjectiveCondition-10000)

#compute linear, quadratic and cubic time in order to compute time trends per condition
linear_time_centered <- (adj_long$time-8)/10
unique(linear_time_centered)
quadratic_time_centered <- linear_time_centered*linear_time_centered
cubic_time_centered <- linear_time_centered*quadratic_time_centered

#compute time trends per condition and filter only the included trials based on incCorr and incZygo
adj_long_inc <- adj_long %>% 
  mutate(t1_moral_pos = ifelse(MoralityValence == 608, linear_time_centered, 0)) %>%  
  mutate(t2_moral_pos = ifelse(MoralityValence == 608, quadratic_time_centered, 0)) %>%  
  mutate(t3_moral_pos = ifelse(MoralityValence == 608, cubic_time_centered, 0)) %>% 
  mutate(t1_immoral_pos = ifelse(MoralityValence == 712, linear_time_centered, 0)) %>%  
  mutate(t2_immoral_pos = ifelse(MoralityValence == 712, quadratic_time_centered, 0)) %>%  
  mutate(t3_immoral_pos = ifelse(MoralityValence == 712, cubic_time_centered, 0)) %>% 
  mutate(t1_moral_neg = ifelse(MoralityValence == 710, linear_time_centered, 0)) %>%  
  mutate(t2_moral_neg = ifelse(MoralityValence == 710, quadratic_time_centered, 0)) %>%  
  mutate(t3_moral_neg = ifelse(MoralityValence == 710, cubic_time_centered, 0)) %>% 
  mutate(t1_immoral_neg = ifelse(MoralityValence == 815, linear_time_centered, 0)) %>%  
  mutate(t2_immoral_neg = ifelse(MoralityValence == 815, quadratic_time_centered, 0)) %>%  
  mutate(t3_immoral_neg = ifelse(MoralityValence == 815, cubic_time_centered, 0)) %>% 
  filter((incCorr==1)&(incZygo==1))

```

The baseline procedure has resulted in an exclusion of `r perc_inc_data`% of the data.

```{r saving the adjective data, eval=FALSE ,echo=FALSE}
# saving the long datafile
write_csv(adj_long_inc, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_state_adjective_trial_data_27-Jun-2023_60pp_preprocessed.csv"))

save(adj_long_inc, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_state_adjective_trial_data_27-Jun-2023_60pp_preprocessed.RData"))
```

# 3. Affect Reason segment

```{r eval=FALSE}

# convert from wide to long format for time and select only corrugator
reason_long <- reason_data_raw %>%
  dplyr::select(!starts_with("AffectReasonZygoPr100ms")) %>% 
  pivot_longer( 
    cols = starts_with("AffectReasonCorrPr100ms"),
    names_to = "time",
    names_prefix = "AffectReasonCorrPr100ms_",
    names_transform = list(time = as.integer),
    values_to = "AffectReason_response"
  )
str(reason_long)

# moral(102)* pos(104), neg(105) = 608, 710 
# immoral(103)* pos(104), neg(105) = 712, 815

# compute relevant factors for the analysis
reason_long <- reason_long %>% 
  mutate(MoralityValence = MoralityCondition*StateAdjectiveCondition-10000)

#compute linear, quadratic and cubic time in order to compute time trends per condition
linear_time_centered <- (reason_long$time-13)/10
unique(linear_time_centered)
quadratic_time_centered <- linear_time_centered*linear_time_centered
cubic_time_centered <- linear_time_centered*quadratic_time_centered

#compute time trends per condition and filter only the included trials based on incCorr and incZygo
reason_long_inc <- reason_long %>% 
  mutate(t1_moral_pos = ifelse(MoralityValence == 608, linear_time_centered, 0)) %>%  
  mutate(t2_moral_pos = ifelse(MoralityValence == 608, quadratic_time_centered, 0)) %>%  
  mutate(t3_moral_pos = ifelse(MoralityValence == 608, cubic_time_centered, 0)) %>% 
  mutate(t1_immoral_pos = ifelse(MoralityValence == 712, linear_time_centered, 0)) %>%  
  mutate(t2_immoral_pos = ifelse(MoralityValence == 712, quadratic_time_centered, 0)) %>%  
  mutate(t3_immoral_pos = ifelse(MoralityValence == 712, cubic_time_centered, 0)) %>% 
  mutate(t1_moral_neg = ifelse(MoralityValence == 710, linear_time_centered, 0)) %>%  
  mutate(t2_moral_neg = ifelse(MoralityValence == 710, quadratic_time_centered, 0)) %>%  
  mutate(t3_moral_neg = ifelse(MoralityValence == 710, cubic_time_centered, 0)) %>% 
  mutate(t1_immoral_neg = ifelse(MoralityValence == 815, linear_time_centered, 0)) %>%  
  mutate(t2_immoral_neg = ifelse(MoralityValence == 815, quadratic_time_centered, 0)) %>%  
  mutate(t3_immoral_neg = ifelse(MoralityValence == 815, cubic_time_centered, 0)) %>% 
  filter((incCorr==1)&(incZygo==1))

```

The baseline procedure has resulted in an exclusion of `r perc_inc_data`% of the data.

```{r saving the reason data, eval=FALSE, echo=FALSE}
# saving the long datafle
write_csv(reason_long_inc, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_affect_reason_trial_data_27-Jun-2023_60pp_preprocessed.csv"))

save(reason_long_inc, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_affect_reason_trial_data_27-Jun-2023_60pp_preprocessed.RData"))
```
