---
title: "EMG4_justice_trait_data"
author: "Marijn Struiksma, Li Kloostra"
date: "`r Sys.Date()`"
output: 
  #pdf_document
  word_document:
    reference_docx: EMG4_template.docx
    toc: yes
    fig_width: 5
    fig_height: 3.5

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "O:/Research/GW/Projects/Jvb-studentprojects/EMG4")
```

## packages
```{r, eval=TRUE, include=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(psych)
```
# Questionnaire 2 data
```{r, eval=TRUE, echo=FALSE}

questionnaire_2 <- read_csv(paste0(getwd(),"/Qualtrics/EMG4_Vragenlijst_2_final.csv"), show_col_types = FALSE) %>%
  slice(-c(1, 2)) %>%
  rename("1" = "1...21",
         '2' = "2...22") %>% 
  select(as.character(c(0,1:17))) %>% 
  mutate_at(as.character(c(0,1:17)), as.numeric) %>% 
  rename(sjCode = "0")

head(questionnaire_2)
```


Select the questions that together measure the construct of Justice

```{r justice question selection, eval=TRUE, echo=TRUE, warning=FALSE}
justiceQs <- questionnaire_2[,-1] 

# Crohnbach's alpha justice questions
# Question 2, 12 and 13 were negatively correlated due to reverse framing. These questions were automatically reversed.
reliability<-psych::alpha(justiceQs, check.keys=TRUE)
reliability
```
The overall Cronbach's alpha is `r reliability$total$raw_alpha`, so we include all questions in our composite Justice score. We do need to reverse the scores for questions 2, 12 and 13.

```{r make justice dataframe centered, eval=TRUE, echo=FALSE}
# create centered scores so it is clear which ratings are fair/neutral/unfair
# But first reverse the scores for Q 2, 12 and 13
head(questionnaire_2)

questionnaire_2_centered <- questionnaire_2 %>%
  mutate(across(c(3,13,14), ~ case_when( #column+1 because column 1 is sjCode
    . == 1 ~ 5,
    . == 2 ~ 4,
    . == 3 ~ 3,
    . == 4 ~ 2,
    . == 5 ~ 1))) %>% 
  mutate(across(c(2:18), ~ case_when(
    . == 1 ~ 2,
    . == 2 ~ 1,
    . == 3 ~ 0,
    . == 4 ~ -1,
    . == 5 ~ -2)))
#head(questionnaire_2_centered)
```

dataframe with only mean justice rating scores (trait score) per participant

```{r mean justice score for selected questions per participant, eval=TRUE, echo=FALSE}
questionnaire_2_means <- questionnaire_2_centered %>%
  pivot_longer(!sjCode, names_to = "Q2", values_to = "J_ratings") %>%
  arrange(sjCode) %>% 
  group_by(sjCode) %>%
  summarise(J_score = mean(J_ratings))

head(questionnaire_2_means)
```

```{r save dataframe with J_means, eval=FALSE, echo=FALSE}
write_csv(questionnaire_2_means, file = paste0(getwd(),"/Qualtrics/justice_means_EMG4_final.csv"))

#read_csv(paste0(getwd(),"/Qualtrics/justice_means_EMG4_final.csv"), show_col_types = FALSE)
```

```{r check scores}
summary(questionnaire_2_means$J_score)
sd(questionnaire_2_means$J_score)
```
```{r histogram}
scatterHist(questionnaire_2_means$J_score,questionnaire_2_means$sjCode)
```

```{r check for outliers}
# https://www.reneshbedre.com/blog/find-outliers.html using Median Absolute Deviation (MAD) 
qqnorm(questionnaire_2_means$J_score)
# get median
med = median(questionnaire_2_means$J_score)
# subtract median from each value of x and get absolute deviation
abs_dev = abs(questionnaire_2_means$J_score-med)
# get MAD
mad = 1.4826 * median(abs_dev)

# get threshold values for outliers
Tmin = med-(3*mad) 
Tmax = med+(3*mad) 

# find outlier
outlier <- questionnaire_2_means$J_score[which(questionnaire_2_means$J_score < Tmin | questionnaire_2_means$J_score > Tmax)]
```

The Justice score `r outlier` is an outlier, therefore, we plot another histogram without the outlier.

```{r remove outlier}
questionnaire_2_means_no_outlier <- questionnaire_2_means %>% 
  filter(J_score > -1)

scatterHist(questionnaire_2_means_no_outlier$J_score,questionnaire_2_means_no_outlier$sjCode)

```

