---
title: "EMG4 post-hoc neutral segment analysis"
author: "Marijn Struiksma"
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: EMG4_template.docx
    toc: yes
    fig_width: 6.5
    fig_height: 4.5
    # We created a word document to implement the html table of the LMM results. We created a pdf from the word document
  # pdf_document:
  #   toc: yes
  #   fig_width: 5
  #   fig_height: 3.5

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_knit$set(root.dir = "O:/Research/GW/Projects/Jvb-studentprojects/EMG4")
```

## Overview

This document contains the preparation of the EMG4 data from the neutral segment for analysis. As well as the post-hoc analysis of the neutral segment in between the state adjective and affect reason segments.

```{r message=FALSE, warning=FALSE }
library(readxl)
library(sjPlot)
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
```

## Load data from all 3 segments

```{r load data,include=F, message=F}
neutral_data_raw <- read_xlsx(paste0(getwd(), "/Matlab/results_paper/EMG4_Bin_Neutral_60sjs.xlsx"))

```

```{r check dataframes, include=F}
head(neutral_data_raw)
```

# 1. Preprocessing Neutral segment

Preprocessing is needed to transform the data from wide to long format based on the 100ms bins for the corrugator response. 
The relevant variables are computed for the different conditions. 
Another MoralityValence variable is computed to estimate the final no-intercept model. 
Furthermore, we've computed linear, quadratic and cubic time trends for each condition (moral, immoral).

```{r eval=FALSE, include=FALSE}

# convert from wide to long format for time and select only corrugator
neutral_long <- neutral_data_raw %>%
  dplyr::select(!starts_with("NeutralZygoPr100ms")) %>% 
  pivot_longer( 
    cols = starts_with("NeutralCorrPr100ms"),
    names_to = "time",
    names_prefix = "NeutralCorrPr100ms_",
    names_transform = list(time = as.integer),
    values_to = "Neutral_response")
str(neutral_long)

# moral(102)* pos(104), neg(105) = 608, 710 
# immoral(103)* pos(104), neg(105) = 712, 815

# compute relevant factors for the analysis
neutral_long <- neutral_long %>% 
  mutate(MoralityValence = MoralityCondition*StateAdjectiveCondition-10000)

#compute linear, quadratic and cubic time in order to compute time trends per condition
linear_time_centered <- (neutral_long$time-13)/10
unique(linear_time_centered)
quadratic_time_centered <- linear_time_centered*linear_time_centered
cubic_time_centered <- linear_time_centered*quadratic_time_centered

#compute time trends per condition and filter only the included trials based on incCorr and incZygo
neutral_long_inc <- neutral_long %>% 
  mutate(t1_moral_pos = ifelse(MoralityValence == 608, linear_time_centered, 0)) %>%  
  mutate(t2_moral_pos = ifelse(MoralityValence == 608, quadratic_time_centered, 0)) %>%  
  mutate(t3_moral_pos = ifelse(MoralityValence == 608, cubic_time_centered, 0)) %>% 
  mutate(t1_immoral_pos = ifelse(MoralityValence == 712, linear_time_centered, 0)) %>%  
  mutate(t2_immoral_pos = ifelse(MoralityValence == 712, quadratic_time_centered, 0)) %>%  
  mutate(t3_immoral_pos = ifelse(MoralityValence == 712, cubic_time_centered, 0)) %>% 
  mutate(t1_moral_neg = ifelse(MoralityValence == 710, linear_time_centered, 0)) %>%  
  mutate(t2_moral_neg = ifelse(MoralityValence == 710, quadratic_time_centered, 0)) %>%  
  mutate(t3_moral_neg = ifelse(MoralityValence == 710, cubic_time_centered, 0)) %>% 
  mutate(t1_immoral_neg = ifelse(MoralityValence == 815, linear_time_centered, 0)) %>%  
  mutate(t2_immoral_neg = ifelse(MoralityValence == 815, quadratic_time_centered, 0)) %>%  
  mutate(t3_immoral_neg = ifelse(MoralityValence == 815, cubic_time_centered, 0)) %>% 
  filter((incCorr==1)&(incZygo==1))

```

```{r saving the neutral data, eval=FALSE, include=FALSE }
# saving the long datafile
write_csv(neutral_long_inc, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_neutral_trial_data_08-Aug-2023_60pp_preprocessed.csv"))

save(neutral_long_inc, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_neutral_trial_data_08-Aug-2023_60pp_preprocessed.RData"))
```

```{r create factors, eval=FALSE, echo=FALSE, include=FALSE}
#Create factor variables:
# moral(102)* pos(104), neg(105) = 608, 710 
# immoral(103)* pos(104), neg(105) = 712, 815

neutral_data <- neutral_long_inc %>% 
  mutate_at(c("MoralityCondition", "StateAdjectiveCondition", "MoralityValence"), as.factor) %>%
  mutate(MoralityCondition = recode(MoralityCondition, "102" = "Moral", "103" = "Immoral")) %>%
  mutate(StateAdjectiveCondition = recode(StateAdjectiveCondition, "104" = "Positive", "105" = "Negative")) %>% 
  mutate(MoralityValence = recode(MoralityValence, "608" = "Moral-Positive", "710" = "Moral-Negative",
                                  "712" = "Immoral-Positive", "815" = "Immoral-Negative"))

```

```{r store mlm data, eval=FALSE, echo=FALSE, include=FALSE}
write_csv(neutral_data, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_neutral_trial_data_for_MLM_analysis_60sjs.csv"))
save(neutral_data, file = paste0(getwd(),"/WORCS_EMG4/data/EMG4_neutral_trial_data_for_MLM_analysis_60sjs.RData"))

```

# 2. MLM Neutral segment

## Building the models
Because our main focus was on the development of the corrugator response over time, we used a growth curve model approach (Mirman, 2015; Peck and Devore, 2008) with specific analysis designs that were optimized for assessing and comparing time trends across conditions. We first modelled participants and items as random factors. To assess the effect of our manipulations on the average activation across an entire segment, we first added morality dimension (moral vs. immoral) as a fixed factor in the model for the character manipulation segment, and morality dimension (moral vs. immoral), critical event valence (positive vs. negative) and interaction as fixed factors in the model for the affective state adjective and affect reason segments. Afterwards the interaction was added to the random part of the model as a random slope. 

Next, linear, quadratic, and cubic trends will be added as covariates in the fixed part of the model, and if significantly improving the model also to the random part, see below. Time trend (e.g. linear) components will be added per condition to maintain flexibility in building the model, and to avoid forcing the model to fit, for example, a linear trend for all conditions when only one condition contains a significant linear component. All trend components will be centered to avoid correlation between trends (fixed effects final model intercepts therefore reflect the average corrugator activity across the entire segment, not the level at which corrugator activity intercepts the y-axis). By using trends up to the cubic component, we achieve some flexibility to fit responses without over-fitting or losing explanatory power (Mirman, 2015). Because we are particularly interested in temporal developments, we will add random slopes for subjects for each time trend that initially improves the model (as well as standard random intercepts for subject and item).

## variables:
dependent variable: Neutral_response
random factors: sjCode, Markertrial  
independent variables: Morality (102=moral, 103=immoral), StateAdjectiveCondition (104=positive, 105=negative), t1_ (continuous linear trend per condition, will be centered for easier interpretation of the estimates), t2_ (continuous quadratic trend per condition, will be centered for easier interpretation of the estimates) , t3_ (continuous cubic trend per condition, will be centered for easier interpretation of the estimates)

```{r load Neutral MLM data, eval=TRUE, echo=FALSE} 
#load data for analysis, previous steps can be skipped.
load(paste0(getwd(),"/WORCS_EMG4/data/EMG4_neutral_trial_data_for_MLM_analysis_60sjs.RData"))
```

```{r building the Neutral models, eval=FALSE, echo=TRUE, include=FALSE}
#empty model
NeutralM1<-lmer(Neutral_response ~ (1|sjCode),data=neutral_data,REML = F);summary(NeutralM1)
NeutralM2<-lmer(Neutral_response ~ (1|sjCode)+(1|Markertrial),data=neutral_data,REML = F);summary(NeutralM2)
anova(NeutralM1,NeutralM2) #p<.001 so NeutralM2 is a better model

# add morality dimension fixed
NeutralM3<-lmer(Neutral_response ~ MoralityCondition +(1|sjCode)+(1|Markertrial),data=neutral_data,REML = F);summary(NeutralM3)
anova(NeutralM2,NeutralM3) #p<.001 sig, so NeutralM3 is a better model

# add state adjective condition fixed
NeutralM4 <- update(NeutralM3, .~.+ StateAdjectiveCondition);summary(NeutralM4)
anova(NeutralM3,NeutralM4) #p<.001 so NeutralM4 is a better model

# add morality dimension*state adjective condition Fixed
NeutralM5 <- update(NeutralM4, .~.+ MoralityCondition:StateAdjectiveCondition);summary(NeutralM5)
anova(NeutralM4,NeutralM5) #p<.001 so NeutralM5 is a better model

# add morality dimension*state adjective condition Random
NeutralM6 <- lmer(Neutral_response ~ MoralityCondition*StateAdjectiveCondition +   
                 (1 + MoralityCondition:StateAdjectiveCondition|sjCode)+(1|Markertrial),data=neutral_data,REML = F, control = lmerControl(optimizer ="Nelder_Mead"));summary(NeutralM6)
#does not converge so NeutralM5 is a better model

# add Immoral_neg Linear Fixed
NeutralM7 <- update(NeutralM5, .~. +t1_immoral_neg );summary(NeutralM7)
anova(NeutralM5,NeutralM7) #p=.07 not sig so NeutralM5 is a better model

# add Immoral_pos Linear Fixed
NeutralM8 <- update(NeutralM5, .~. +t1_immoral_pos );summary(NeutralM8)
anova(NeutralM5,NeutralM8) #p<.001 sig, so NeutralM8 is a better model

# add Moral_neg Linear Fixed
NeutralM9 <- update(NeutralM8, .~. +t1_moral_neg );summary(NeutralM9)
anova(NeutralM8,NeutralM9) #p=.28 not sig so NeutralM8 is a better model

# add Moral_pos Linear Fixed
NeutralM10 <- update(NeutralM8, .~. +t1_moral_pos );summary(NeutralM10)
anova(NeutralM8,NeutralM10) #p=.96 not sig so NeutralM8 is a better model

# add Immoral_pos Linear Random
NeutralM11 <- lmer(Neutral_response ~ MoralityCondition*StateAdjectiveCondition + t1_immoral_pos + (1 + t1_immoral_pos|sjCode)+(1|Markertrial),data=neutral_data,REML = F, control = lmerControl(optimizer ="Nelder_Mead"));summary(NeutralM11)
anova(NeutralM10,NeutralM11) #p<.001 so NeutralM11 is a better model

# add Immoral_neg Quadratic Fixed
NeutralM12 <- update(NeutralM11, .~. +t2_immoral_neg );summary(NeutralM12)
anova(NeutralM11,NeutralM12) #p=.11 not sig so NeutralM11 is a better model

# add Immoral_pos Quadratic Fixed
NeutralM13 <- update(NeutralM11, .~. +t2_immoral_pos );summary(NeutralM13)
anova(NeutralM11,NeutralM13) #p=.03 sig so NeutralM13 is a better model

# add Moral_neg Quadratic Fixed
NeutralM14 <- update(NeutralM13, .~. +t2_moral_neg );summary(NeutralM14)
anova(NeutralM13,NeutralM14) #p=.37 not sig so NeutralM13 is a better model

# add Moral_pos Quadratic Fixed
NeutralM15 <- update(NeutralM13, .~. +t2_moral_pos );summary(NeutralM15)
anova(NeutralM13,NeutralM15) #p=.16 not sig so NeutralM13 is a better model

# add Immoral_pos Quadratic Random
NeutralM16 <- lmer(Neutral_response ~ MoralityCondition*StateAdjectiveCondition + t1_immoral_pos + t2_immoral_pos  + (1 + t1_immoral_pos + t2_immoral_pos |sjCode) + (1|Markertrial), data=neutral_data,REML = F, control = lmerControl(optimizer ="Nelder_Mead"));summary(NeutralM16)
#does not converge, so NeutralM13 is a better model

# add Immoral_neg Cube Fixed
NeutralM17 <- update(NeutralM13, .~. +t3_immoral_neg );summary(NeutralM17)
anova(NeutralM13,NeutralM17) #p=.52 not sig so NeutralM13 is a better model

# add Immoral_pos Cube Fixed
NeutralM18 <- update(NeutralM13, .~. +t3_immoral_pos );summary(NeutralM18)
anova(NeutralM13,NeutralM18) #p=.96 not sig so NeutralM13 is a better model

# add Moral_neg Cube Fixed
NeutralM19 <- update(NeutralM13, .~. +t3_moral_neg );summary(NeutralM19)
anova(NeutralM13,NeutralM19) #p=.92 not sig so NeutralM13 is a better model

# add Moral_pos Cube Fixed
NeutralM20 <- update(NeutralM13, .~. +t3_moral_pos );summary(NeutralM20)
anova(NeutralM13,NeutralM20) #p=.84 not sig so NeutralM13 is the best model

```

```{r save the best Neutral model, eval=FALSE, echo=FALSE}
save(NeutralM13, file = paste0(getwd(),"/WORCS_EMG4/results/EMG4_Neutral_final_model_60sjs.RData"))

```

### Summary of best Model NeutralM13
The best model is Model 13: Neutral_response ~ MoralityCondition + StateAdjectiveCondition  + MoralityCondition:StateAdjectiveCondition + t1_immoral_pos + t2_immoral_pos + (1 + t1_immoral_pos | sjCode) + (1 | Markertrial). This is the summary of that model.

```{r summary, eval=TRUE}
load(paste0(getwd(),"/WORCS_EMG4/results/EMG4_Neutral_final_model_60sjs.RData"))
summary(NeutralM13)
```

```{r Neutral  table, eval=FALSE, echo=FALSE, include=FALSE}
# code to generate HTML table, run manually and can be copied into manuscript
tab_model(NeutralM13,
          collapse.ci=TRUE, show.stat=TRUE, digits.p=3, ci.hyphen=",&nbsp;", 
          dv.labels = "Neutral Segment",
          show.loglik=TRUE, show.dev=TRUE, show.r2=FALSE, show.obs=FALSE,
          show.df=TRUE, title="Summary of LMM of Neutral segment." )

```

### Post-hoc analyses

```{r post-hoc explore the Neutral interaction, eval=TRUE}
NeutralM13_emmeans_contrasts = emmeans(NeutralM13,specs = tukey ~ MoralityCondition * StateAdjectiveCondition, lmer.df = "satterthwaite", lmerTest.limit=93500, simple = "each", combine = T, adjust = "sidak", reverse = T)
NeutralM13_emmeans_contrasts$emmeans
NeutralM13_emmeans_contrasts$contrasts %>%
     summary(infer = TRUE)

```

Plot of regression lines for the different State Adjectives for the Morality manipulation in the Affect Reason segment:

```{r figure Neutral, eval=TRUE, echo=FALSE, fig.cap = "Figure on neutral segment with CI", warning=FALSE}
emmip(NeutralM13,StateAdjectiveCondition~MoralityCondition, CIs = TRUE) + scale_color_manual(values=c("#009E73","#D55E00"))
```

The comparison between t1_immoral_pos and t2_immoral_pos is redundant since they refer to different time trends. However, the negative t1 component indicates a downward slope with a rise-fall pattern, as indicated by the positive t2 component.

# 3. Figures

```{r ggplot specs, echo=FALSE}
#colorpalette
# MoralPos, MoralNeg, ImmoralPos, ImmoralNeg
colors_moral_valence <- c("Moral-Negative" = "#252525","Moral-Positive" = "#969696","Immoral-Negative" = "#252525","Immoral-Positive" = "#969696")

# line types
lines_moral_valence <- c("Moral-Positive" = "solid", "Moral-Negative" = "solid", "Immoral-Positive" = "dashed", "Immoral-Negative" = "dashed")

#shapes 
shape_moral_valence <-c("Immoral-Negative" = "triangle filled", "Immoral-Positive" = "triangle open", "Moral-Negative" = "square filled", "Moral-Positive" = "square open")

#legend labels - Morality x Valence + Reason
morvalreason_fit_labels <- c(expression(paste("model fit,   Moral-Pos: e.g., [Good Mark] \"...", italic("[happy ]"),                                          "[when ... ] ", italic("he spots a petrol station"), "\"")),
                             expression(paste("model fit,   Moral-Neg: e.g., [Good Mark] \"...", italic("[frustrated ]"),                                     "[when ... ] ", italic("he runs out of petrol"), "\"")),
                             expression(paste("model fit,   Immoral-Pos: e.g., [Bad Mark]\"...", italic("[happy ]"),
                                    "[when ... ] ", italic("he spots a petrol station"), "\"")),
                             expression(paste("model fit,   Immoral-Neg: e.g., [Bad Mark] \"...", italic("[frustrated ]"),                                     "[when ... ] ", italic("he runs out of petrol"), "\"")))
#legend labels - Morality x Valence +neutral+  Reason
morvalneutralreason_fit_labels <- c(expression(paste("model fit,   Immoral-Neg: e.g., [Bad Mark] \"...",
                             italic("[frustrated ]"),"[when ... ] ", italic("he runs out of petrol"), "\"")),
                             expression(paste("model fit,   Immoral-Pos: e.g., [Bad Mark]\"...", italic("[happy ]"),
                                    "[when ... ] ", italic("he spots a petrol station"), "\"")),
                             expression(paste("model fit,   Moral-Neg: e.g., [Good Mark] \"...", italic("[frustrated ]"),                                     "[when ... ] ", italic("he runs out of petrol"), "\"")),
                             expression(paste("model fit,   Moral-Pos: e.g., [Good Mark] \"...", italic("[happy ]"),                                          "[when ... ] ", italic("he spots a petrol station"), "\"")))

```

## Neutral segment

```{r prepare data corrugator neutral segment, echo=FALSE}
# load state adjectiveneutral trial data and final model to get predicted values
load(paste0(getwd(),"/WORCS_EMG4/data/EMG4_neutral_trial_data_for_MLM_analysis_60sjs.RData"))
load(paste0(getwd(),"/WORCS_EMG4/results/EMG4_Neutral_final_model_60sjs.RData"))
predicted_values_neutral<- modelr::add_predictions(neutral_data, NeutralM13) 

predicted_values_neutral_plot <- predicted_values_neutral %>% 
  group_by(MoralityValence, time) %>% 
  summarise(Neutral_response_M = mean(Neutral_response), Neutral_response_SD =
              sd(Neutral_response), Neutral_pred_M = mean(pred), Neutral_pred_SD = sd(pred)) 

```

```{r save the corrugator neutral data, eval=FALSE, echo=FALSE}
save(predicted_values_neutral_plot, file =
       paste0(getwd(),"/WORCS_EMG4/data/EMG4_Corrugator_neutral_plot_data_60sjs.RData"))

#load(paste0(getwd(),"/WORCS_EMG4/data/EMG4_Corrugator_neutral_plot_data_60sjs.RData"))

```



```{r plot reason, echo = F, message =F, warning =F}
# plot the predicted values as a line and the raw data as points
tiff(paste0(getwd(), "/WORCS_EMG4/images/corr_neutral_pred_overlay.tiff"), units="cm", width=20, height=15, res=300)
predicted_values_neutral_plot %>%   
  mutate(timeSec = (time-0.5)/10) %>% 
  ggplot(aes(timeSec, Neutral_pred_M))+
  geom_line(aes(linetype=MoralityValence, color = MoralityValence, shape = MoralityValence), size=0.5)+
  geom_point(aes(timeSec, Neutral_response_M, shape = MoralityValence),color = "#666666", fill = "#252525", 
             size = 0.8)+
  scale_color_manual(name = "test", labels=morvalreason_fit_labels, values = colors_moral_valence, 
                     guide = guide_legend(reverse = F))+
  scale_linetype_manual(name = "test", labels=morvalreason_fit_labels, values = lines_moral_valence, 
                     guide = guide_legend(reverse = F))+
  scale_shape_manual(name = "test", labels=c("observed data","observed data","observed data","observed data"), 
                     values = shape_moral_valence)+
  scale_x_continuous(breaks = seq(0,2.6,.5), limits = c(0,2.5)) +
  scale_y_continuous(breaks = seq(100,160,10), limits = c(95,160))+
  labs(#title = "Corrugator Response at Neutral Segment",
       x = "Time in seconds",
       y = "Response as % of baseline")+
  theme_classic()+   
  theme(text = element_text(family="sans"),
        legend.position ="bottom",
        legend.direction = 'vertical',
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.text.align = 0)
dev.off()

```

## Adjective + neutral + reason

```{r prepare data corrugator adjective + reason segment, eval=F, echo = F, message =F, warning =F}
#load(paste0(getwd(),"/WORCS_EMG4/data/EMG4_Corrugator_adjective_plot_data_60sjs.RData"))
#load(paste0(getwd(),"/WORCS_EMG4/data/EMG4_Corrugator_reason_plot_data_60sjs.RData"))
load(paste0(getwd(),"/WORCS_EMG4/data/EMG4_Corrugator_adjective_reason_plot_data_60sjs.RData"))

neutral_pred_plot <- predicted_values_neutral_plot %>% 
  mutate(timeBinAR = time+49)

adj_neutral_reason_corr_plot <- adj_reason_corr_plot %>% 
  full_join(y=neutral_pred_plot, by = c("timeBinAR","MoralityValence")) %>% 
  mutate(Corrugator_response = case_when(StateAdjective_response_M > 0 ~ StateAdjective_response_M,
                                         AffectReason_response_M > 0 ~ AffectReason_response_M,
                                         Neutral_response_M > 0 ~ Neutral_response_M,
                                         .default = Corrugator ))

```

```{r save the corrugator adjective + neutreal + reason data, eval=FALSE, echo=FALSE}
save(adj_neutral_reason_corr_plot, file =
       paste0(getwd(),"/WORCS_EMG4/data/EMG4_Corrugator_adjective_neutral_reason_plot_data_60sjs.RData"))

```

```{r plot adjective and reason, echo = F, message =F, warning =F}
load(paste0(getwd(),"/WORCS_EMG4/data/EMG4_Corrugator_adjective_neutral_reason_plot_data_60sjs.RData"))

#tiff(paste0(getwd(), "/WORCS_EMG4/images/corr_adj_neutral_reason_pred_overlay.tiff"), units="cm", width=20, height=15, res=300)
adj_neutral_reason_corr_plot %>%   
  mutate(timeSec = (timeBinAR+0.5)/10) %>% 
  ggplot(aes(timeSec, StateAdjective_pred_M))+
  geom_line(aes(linetype=MoralityValence, color = MoralityValence, shape = MoralityValence), size=0.5)+
  geom_point(aes(timeSec, Corrugator_response, shape = MoralityValence), color = "#666666", fill = "#252525", size = 0.8)+
  geom_line(aes(timeSec, AffectReason_pred_M, linetype=MoralityValence, color = MoralityValence, shape = MoralityValence),
            size=0.5)+
  geom_line(aes(timeSec, Neutral_pred_M, linetype=MoralityValence, color = MoralityValence, shape = MoralityValence),
            size=0.5)+
  scale_color_manual(name = "test", labels=morvalneutralreason_fit_labels, values = colors_moral_valence, 
                     guide = guide_legend(reverse = T))+
  scale_linetype_manual(name = "test", labels=morvalneutralreason_fit_labels, values = lines_moral_valence, 
                        guide = guide_legend(reverse = T))+
  scale_shape_manual(name = "test", labels=c("observed data","observed data","observed data","observed data"), 
                     values = shape_moral_valence, guide = guide_legend(reverse = T))+
  scale_x_continuous(breaks = seq(0,10,.5), limits = c(0,10)) +
  scale_y_continuous(breaks = seq(100,160,10), limits = c(95,165))+
  labs(title = "Corrugator Response at Affective Event",
       x = "Time in seconds",
       y = "Response as % of baseline")+
  theme_classic()+   
  theme(legend.position="bottom",
        legend.direction = 'vertical',
        legend.title = element_blank(),
        legend.text.align = 0)+
  geom_vline(xintercept = c(0.25, 1.25, 1.5, 2.25, 2.5, 3.25, 3.5, 4.5, 4.75, 7.25, 7.5, 10), size=0.2, alpha = .5) +
  annotate("rect", xmin = 3.5, xmax = 5, ymin = 95, ymax = 165, alpha = .1) +  # shaded area to show analyzed frame adjective segment
  annotate("rect", xmin = 7.5, xmax = 10, ymin = 95, ymax = 165, alpha = .1) +  # shaded area to show analyzed frame reason segment
  annotate("text", x = 0.8, y = 160, label="[...]", size = 3) +
  annotate("text", x = 1.9, y = 160, label="[Name]", size = 3) +
  annotate("text", x = 2.9, y = 160, label="[Verb]", size = 3) +
  annotate("text", x = 4, y = 160, label="State\nAdjective", size = 3) +
  annotate("text", x = 6, y = 160, label="[Neutral Segment]", size = 3) +  
  annotate("text", x = 8.8, y = 160, label="Affect\nReason", size = 3) 
#dev.off()
```