---
title: "EMG4_analysis_behavioral_data.pdf"
author: "Marijn Struiksma, Li Kloostra"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: yes
    fig_width: 5
    fig_height: 3.5

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "O:/Research/GW/Projects/Jvb-studentprojects/EMG4")
```

## R packages

```{r packages, echo=F, message=F}
library(ggthemes)
library(ggplot2)
library(tidyverse)
library(readxl)
```


## Embedded Ratings

```{r load behavioral data, include=FALSE}
embedded_data <- read_csv(paste0(getwd(), "/Python/output_for_analysis/embedded_ratings_60sjs_20230202.csv")) %>% 
  select(subjectcode:RT) %>% 
  rename(sjCode=subjectcode) %>% 
  rename(Markertrial=trialnr) %>%  
  rename(embed_rating=rating) %>% 
  rename(embed_RT=RT)
head(embedded_data)

```

```{r checking the embedded ratings}
# number of NA responses
sum(is.na(embedded_data$embed_rating))

table(embedded_data$embed_rating)

```

```{r markertrials with NA embedded ratings per participant, include=F}
NA_ratings <- embedded_data %>%
  select(sjCode, Markertrial, embed_rating) %>% 
  filter(is.na(embed_rating)) %>%
  group_by(sjCode, Markertrial) %>%
  summarise(Freq = n())

head(NA_ratings)
```

RT ratings\
nb:remove NA values from trials with missing ratings

```{r compute embedded ratings}
embedded_ratings <- embedded_data %>%
  select(sjCode, Markertrial, embed_rating, embed_RT) %>%  
  filter(!is.na(embed_rating))
head(embedded_ratings)
```

ratings per participant

```{r boxplot ratings per PP, echo =F}
boxplot_ratings_pp <- ggplot(embedded_ratings, aes(x = as.factor(sjCode), y = embed_rating)) +
  scale_y_continuous(n.breaks = 7) +
  theme(axis.text.x= element_text(angle = 90, vjust = 0.5)) +
  geom_boxplot()  +
  labs(title = "Ratings on embedded rating task per participant",
       x = "Participant", y = "Embedded Rating") 
boxplot_ratings_pp
```

Rating times


```{r boxplot RT ratings per PP, echo =F}

summary(embedded_ratings$embed_RT)

RT_ratings_plot <- ggplot(embedded_ratings, aes(x = as.factor(sjCode), y = embed_RT)) +
#  scale_y_continuous(n.breaks = 7) +
  theme(axis.text.x= element_text(angle = 90, vjust = 0.5)) +
  geom_boxplot()  +
  labs(title = "Response times on on embedded rating task per participant",
       x = "Participant", y = "Response time on embredded rating task (ms)") 
RT_ratings_plot
```

# Fairness ratings

```{r load fairness data}
fairness_data <- read_csv(paste0(getwd(), "/Qualtrics/fairness_all_EMG4_final.csv")) %>% 
  rename(fairness_rating = F_rating)
```


```{r checking the fairness ratings}
# number of NA responses
sum(is.na(fairness_data$fairness_rating))

table(fairness_data$fairness_rating)

```
```{r compute fairness ratings}
fairness_ratings <- fairness_data %>% 
  filter(!is.na(fairness_rating))
table(fairness_ratings$fairness_rating)

```

```{r boxplot fairness ratings per PP, echo =F}
boxplot_fairness_ratings_pp <- ggplot(fairness_ratings, aes(x = as.factor(sjCode), y = fairness_rating)) +
  scale_y_continuous(n.breaks = 7) +
  theme(axis.text.x= element_text(angle = 90, vjust = 0.5)) +
  geom_boxplot()  +
  labs(title = "Ratings on fairness rating task per participant",
       x = "Participant", y = "Fairness Rating") 
boxplot_fairness_ratings_pp
```

# Justice scores

```{r load justice data, include=FALSE}
justice_means <- read_csv(paste0(getwd(), "/Qualtrics/justice_means_EMG4_final.csv")) %>% 
  mutate_at("sjCode", as.numeric) %>% 
  rename(justice_score = J_score)
```


```{r checking the justice scores}
# number of NA responses
summary(justice_means$justice_score)

```

```{r histogram justice scores, echo =F}
scatterplot_justice_scores <- ggplot(justice_means, aes(x = sjCode, y = justice_score)) +
  scale_y_continuous(n.breaks = 7) +
  # theme(axis.text.x= element_text(angle = 90, vjust = 0.5)) +
  geom_point() +
  labs(title = "Justice score per participant",
       x = "Participant", y = "Justice Score") 
scatterplot_justice_scores

```

```{r check justice outliers}
justice_means_z <- justice_means %>% 
  mutate(justice_score_z = scale(justice_means$justice_score)) 

justice_means_z <- justice_means_z %>% 
  mutate(justice_score_z = justice_means_z$justice_score_z[,1])

summary(justice_means_z)

hist(justice_means_z$justice_score_z, breaks = seq(-4,2, by=0.5))

# finding the extreme outliers in the justice score
justice_means_z[abs(justice_means_z$justice_score_z)>(1.98),]
```

# comprehension questions check
check number of trials with incorrect comprehension responses per participant

```{r load comprehension data, include=FALSE}
#comprehension_exit_data_combined <- read_csv(paste0(getwd(), "/WORCS_EMG4/data/EMG4_comprehension_exit_data_combined_60sjs.csv"),show_col_types = FALSE)
comprehension_data <- read_csv(paste0(getwd(), "/Python/output_for_analysis/comprehension_questions_60sjs_20230202.csv")) %>% 
  select(subjectcode:correct) %>% 
  rename(sjCode=subjectcode) %>% 
  rename(comp_response=response) %>% 
  rename(comp_RT=RT) %>% 
  rename(comp_correct=correct)
head(comprehension_data)

```

```{r Checking the comprehension questions, include=T}
# check how many questions were correct (1) and incorrect (1)
table(comprehension_data$comp_correct)  
#  check comprehension questions, for keys used (1 and 7 were the response keys) 
table(na.omit(comprehension_data$comp_response))  

# check number of missed responses
NA_questions <- comprehension_data %>%
  select(sjCode, questionnr, comp_response) %>% 
  filter(is.na(comp_response)) %>%
  group_by(sjCode, questionnr) %>%
  summarise(Freq = n())

head(NA_questions) # only 6 missings

# check number of erroneous key 2 used
Resp2_questions <- comprehension_data %>%
  select(sjCode, questionnr, comp_response) %>% 
  filter(comp_response==2) %>%
  group_by(sjCode, questionnr) %>%
  summarise(Freq = n())

head(Resp2_questions) # only 6 erroneous keys used

# On 6 occasions a response 2 has been given, 
# this is not a valid response and needs to be corrected to NA.
comprehension_data_clean <- comprehension_data %>% 
  select((sjCode:comp_correct)) %>% 
  mutate(comp_RT = if_else(comp_response==2, NA, comp_RT))%>% 
  mutate(comp_correct = if_else(comp_response==2, NA, comp_correct))

```



number and percentage of comprehension questions answered correctly per participant

```{r add column percentages correct}
corr_comp_perc <- comprehension_data_clean %>%
  select(sjCode, comp_correct) %>%
  group_by(sjCode) %>%
  summarise(sum_CorrComp = sum(comp_correct, na.rm = TRUE)) %>% 
  mutate(comp_percentage = sum_CorrComp/12*100)

head(corr_comp_perc)

```

```{r PP with <60% correct responses}
corr_comp_perc %>%
  filter(comp_percentage < 60.5)
```


create barplot:

```{r barplot comprehension questions, echo =F}

barplot_corr <- ggplot(corr_comp_perc, aes(x = as.character(sjCode), y = comp_percentage, fill = comp_percentage)) +
  geom_bar(stat = 'identity') +
  scale_y_continuous(breaks = seq(0,100,by=5))  +
  geom_hline(yintercept = 50, linetype = "dashed") +
  labs(title = "Percentage of comprehension questions answered correctly per participant",
       x = "Participant", y = "%") +
  theme(panel.grid = element_blank(),
        axis.text.x= element_text(angle = 90, vjust = 0.5),
        legend.position = "none",
        panel.grid.major.y = element_line(color = 'grey'))
barplot_corr
```

```{r, echo=FALSE}

#ggsave(file = "../figures/Barplot_corr_comp_31-08-2022.pdf", barplot_corr,
#       width = 25, height = 15, unit = 'cm', dpi = 300)

```

# check RT times on comprehension questions

```{r correct comprehension questions per PP}
summary(comprehension_data_clean$comp_RT)

RT_comp <- comprehension_data_clean %>%
  drop_na() %>% 
  arrange(comp_RT)

head(RT_comp)
```

```{r}

barplot_RT_comp <- ggplot(RT_comp, aes(x = as.character(sjCode), y = comp_RT)) +
  geom_boxplot() +
  scale_y_continuous(n.breaks = 10)  +
  labs(title = "Response time of comprehension question answers per participant",
       x = "Participant", y = "Response time (ms)") +
  theme(axis.text.x= element_text(angle = 90, vjust = 0.5))

barplot_RT_comp
```

